The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-07-29 brains-introduction.tex
feat/start: rewrite abstract

TOO GENERAL OR GIVES THE IMPRESSION OF TOO HIGH AMBITIONS. COMPARE TO OTHER INTROS TO JUST SAY WE'LL TALK ABOUT THIS.

Since the very beginnings of both social science and psychology, scientists have tried to capture the way cognition and culture influence each other.
%the reciprocal influences of cognition and culture in meaningful ways.
While this has been the subject of intense debate in the social sciences in the 20th century (starting with Durkheim's initial works, \citeyear{durkheim_les_1912}, later tackled in earnest by \hbox{e.g.} Mauss' \emph{Techniques of the Body}, \citeyear{mauss_les_1936}, Giddens' \emph{Structuration Theory}, \citeyear{giddens_constitution_1984}, and Bourdieu's \emph{Sens Pratique}, \citeyear{bourdieu_sens_1980}), today's discussion is mostly structured by proponents from cognitive science.

>>>>

Since the very beginnings of both social science and psychology, scientists have tried to capture the way cognition and culture influence each other.
The question has been the subject of intense debate in the social sciences in the 20th century (starting with Durkheim's initial works, \citeyear{durkheim_les_1912}, later tackled in earnest by \hbox{e.g.} Mauss' \emph{Techniques of the Body}, \citeyear{mauss_les_1936}, Giddens' \emph{Structuration Theory}, \citeyear{giddens_constitution_1984}, and Bourdieu's \emph{Sens Pratique}, \citeyear{bourdieu_sens_1980}), but today's discussion is mostly structured by proponents from cognitive science.

### 2016-07-29 brainscopycut.tex
feat/substitution-models: finish first rewrite of substitution models
feat/results: finish variation subsection
feat/results: finish presentation of results
feat/start: rewrite abstract

% Mathematics and Code
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[group-separator={,}]{siunitx}
%\usepackage{stmaryrd}
\usepackage{xfrac}
\usepackage{mathtools}
%\newcommand{\defeq}{\overset{\underset{\mathrm{def}}{}}{=}}

@@

% Have graphics
\graphicspath{{images/}}
\usepackage{graphicx}
\usepackage{subfig}

@@

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{We describe reformulation processes within a large distributed system such as blogspace;
showing how some specific features of public representations may be altered by bloggers when they freely reproduce them.
To deal with robust and simple cultural representations, we focus on the evolution of quotations.
In particular, we uncover some of the semantic and structural characteristics of individual words and the substitutions they undergo.
Our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
We show that all variables remarkably exhibit a single attractor and are generally contractile.
Even though the observed convergence patterns only partially explain quotation evolution, we shed light on a class of phenomena which are prone to constitute a key element of a broader empirically-grounded, attractor-based theory of cultural evolution.
\todo{Update after introduction rework.}}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{word production; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

%\clearpage
%\input{brains-garbage}

>>>>

% Mathematics and Code
\usepackage{amsmath}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage[group-separator={,}]{siunitx}
%\usepackage{stmaryrd}
\usepackage{xfrac}
\usepackage{mathtools}
%\newcommand{\defeq}{\overset{\underset{\mathrm{def}}{}}{=}}

@@

% Have graphics
\graphicspath{{images/}}
\usepackage{graphicx}
%\usepackage{subfig}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}

@@

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{
We present a case study which connects psycholinguistics with the field of cultural evolution, in order to test for the existence of cultural attractors in the evolution of quotations online.
Such attractors have been suggested as a useful tool for the study of cultural evolution and its reciprocal influences with cognition, but their existence has been hard to test.
Our study focuses on how quotations are transformed when they are copied from blog to blog or media website:
by coding words with a number of well-studied lexical features, we show that the way words are substituted in quotations is consistent (1) with the hypothesis of cultural attractors, and (2) with known effects of the word features.
In particular, words known to be harder to recall in lists have a higher tendency to be substituted, and words easier to recall are produced instead.
Our results support the hypothesis that cultural attractors can arise from the combination of individual cognitive biases in interpretation and production of representations.
}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{\newtext{word recall}; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

@@

%\clearpage
\appendix
\input{brains-appendix}
